%% start of file `cv.tex'.
%% Based on `template.tex` from the moderncv distribution by Xavier Danaux
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.



\documentclass[11pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{carlos}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                  % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                         % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}      % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Carlos}
\familyname{Quiros}
%\title{A great man}                          % optional, remove / comment the line if not wanted
% \address{Nairobi}{Kenya}    % optional, remove / comment the line if not wanted
\mobile{+254 728673771 / +506 61541180 }                     % optional, remove / comment the line if not wanted
\email{cquiros@qlands.com}                          % optional, remove / comment the line if not wanted
\social[linkedin]{https://cr.linkedin.com/in/qlands}                        % optional, remove / comment the line if not wanted
\social[github]{https://github.com/qlands}                              % optional, remove / comment the line if not wanted
%\homepage{www.qlands.com}
%\extrainfo{www.qlands.com/cquirosDetailedCV.pdf}            % optional, remove / comment the line if not wanted
\quote{\normalfont{\restoregeometry{Nineteen years experience in Information Communication Technologies (ICTs) in different capacities ranging from technical to managerial with over twelve years supporting international agricultural research and development. Career interests have evolved from implementing tasks related to agricultural software programming, to more managerial activities in area of research data management and providing strategic guidance on how ICTs can address global agricultural challenges. Currently consulting research and development organisations like Bioversity International and CSIRO. Experience includes a long term posting in Kenya (eleven years with ILRI), one years as an advisor on ICTs for various organisations in East Africa and seven years with the private sector in Costa Rica.}}}                            % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                     % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2006--2007}{\textbf{MA}\normalfont{ Science and Technologies Studies}}{University of Maastricht}{The Netherlands}{}{\textit{Dissertation on The Socio-Technical Aspects Affecting the Adoption of Agricultural Information Systems.}}  % arguments 3 to 6 can be left empty
\cventry{1998--2002}{\textbf{BSc}\normalfont{ Computer Engineering}}{Universidad Latinoamérica de Ciencia y Tecnología}{Costa Rica}{}{}  % arguments 3 to 6 can be left empty

\section{Experience}
\subsection{International Consultant on ICTs for Development (ICT4D) and Research Data Management (RDM)}
\cventry{To date}{Bioversity International}{}{Turrialba, Costa Rica}{}{\textit{Advice Bioversity International in the development of biodiversity ICTs.}
  \begin{itemize}
  \item Help Bioversity in setting up ICT priorities, strategies and best practices.
  \item Lead the development of online and mobile crowd-sourcing systems for testing and validating biodiversity crop trials.
  \end{itemize}}
\cventry{}{International Livestock Research Institute (ILRI)}{}{Nairobi, Kenya}{}{\textit{Advice and support ILRI in implementing ICT4D projects and RDM Systems. }
  \begin{itemize}
  \item Design and implement business models for sustainable ICT4D platforms.
  \item Support research projects in implementing their data management strategy.
  \item Maintain ILRI's RDM system.
  \item Represent ILRI on the CGIAR Data Management Taskforce.
  \end{itemize}}
\cventry{}{Other consultancies}{}{}{}{\textit{Supporting research and development organisations in implementing ICTs}
  \begin{itemize}
  \item For CABI Africa: Adapt and implement CKAN for organising and making available fertilizing trials.
  \item For CSIRO: Develop an online portal for modelling livestock feeding strategies. 
  \end{itemize}}
\subsection{Previous positions}
\cventry{2011--2015}{Agricultural Information System Specialist}{ILRI}{Nairobi, Kenya}{}{\textit{Lead activities in the area of ICT4D and RDM.}
  \begin{itemize}
  \item Oversee the data management of more than 15 research projects.
  \item Supervise seven staff members including programmers, data managers and clerks.
  \item Design, implement and manage 16 ICT-RDM projects.
  \item Assess progress and report targets to higher management levels.
  \item Define the strategic direction and priorities for the institute in the area of ICT4D and RDM.
  \end{itemize}}
\cventry{2010--2011}{Consultant on ICTs for Research and Development}{}{Nairobi, Kenya}{}{{}
  \begin{itemize}
  \item For ASARECA: Provide strategic and technical leadership on integrating ICTs into their Knowledge and Communication Strategy.
  \item For FAO: Lead the development of the Livestock Drought Management software. 
  \item For the University of Edinburgh: Redesign the database for the project on Infectious Diseases of East African Livestock.
  \item For ILRI: Implement diverse data management tools.  
  \end{itemize}}
\cventry{2003--2009}{Visiting Scientist}{ILRI}{Nairobi, Kenya}{}{{}
\begin{itemize}
\item Lead sociological research related to the dissemination and adoption of livestock knowledge.
\item Programme diverse agricultural information systems.
\end{itemize}}
\cventry{1996--2003}{Software Developer}{Sistemas del Orbe}{Costa Rica}{}{{}
\begin{itemize}
  \item Programme software in the banking and manufacturing sectors for companies such as Credomatic, Yamber, Demasa and BICSA, among others.    
  \end{itemize}}

\section{Languages}
\cvitem{Spanish}{Mother tongue}
\cvitem{English}{Full professional proficiency}
\cvitem{French}{Elementary proficiency}

\section{Skills}
\cvitem{Managerial}{Project management, Team management and leadership, Agile methodologies}
\cvitem{Programming}{C++, Python, Java, JavaScript, CSS, HTML5}
\cvitem{Databases}{MySQL, Oracle, MS SQL, PostgreSQL}
\cvitem{Platforms}{Linux, Windows, Android}

\section{Key information systems developed}
\cvitem{ODK Tools}{A toolbox for automating Research Data Management using ODK and MySQL databases. Available at https://github.com/ilri/odktools}
\cvitem{ODK Viewer}{An Android App to visualise ODK data on mobile devices. Available at https://github.com/ilri/odkviewer}

\section{Key publications}
\cvitem{2015}{Quiros C. and Poole J. \textit{ILRI Data Management Policy}. Available at https://cgspace.cgiar.org/handle/10568/63496}
\cvitem{2009}{Quiros C., Thornton P. K., Herrero M., Notenbaert A. and Gonzalez-Estrada E. \textit{GOBLET: An open-source geographic overlaying database and query module for spatial targeting in agricultural systems}. Computers and Electronics in Agriculture, 68(1)}
\cvitem{2007}{Herrero M., González-Estrada E., Thorton P. K., Quiros C., Waithaka M. M., Ruiz R. and Hoogenboom G. \textit{IMPACT: Generic household databases and diagnostics tools for integrated crop – livestock systems analysis}. Agricultural Systems, 92(1-3)}

\section{References}
\cvitem{Dr Mario Herrero}{Chief Research Scientist. CSIRO. \textit{mario.herrero@csiro.au}}
\cvitem{Ms Jane Poole}{Leader Research Methods Group. ILRI. \textit{j.poole@cgiar.org}}
\cvitem{Dr Roger Day}{Deputy Director for Development. CABI. \textit{r.day@cabi.org}}

\end{document}


%% end of file `cv.tex'.
